---
title: "R Notebook"
output: html_notebook
---

### To Run this code in a command line, please define the location to "RScript.exe" with the following code:
#### set R_Script="C:\Program Files\R\R-3.4.1\bin\RScript"
#### Note: The path to your RScript may be different. Please update it and run that line first in order to run R in the command line.

Load packages

  Lubridate: Extrate dates
  Dplyr: Transform Data
  Readr: Read csv files
  
```{r}
require(lubridate)
require(dplyr)
require(readr)
```

Argument 1: Inspection Data
Argument 2: Location Data
Argument 3: New File

Note: When you pass the files into new_complaints.R, be sure to include the entire file name. The argument must be "filename.csv", not "filename".

```{r}
args <- commandArgs(trailingOnly = TRUE)

inspections <- read_csv("potential_inspection_summary_data.csv")
location <- read_csv("inspection_geocodes_w_block.csv") # created using add_census_block_data.R from DropBox

# add new cols
inspections$census_block <- location$census_block
inspections$year <- year(inspections$inspection_date)
inspections$week <- week(inspections$inspection_date)

# process inspection_type string
inspections$inspection_type <- tolower(inspections$inspection_type)


# filter and count
data <- inspections %>%
    select(establishment_type, establishment_name, risk_category, year, week, census_block, inspection_type) %>%
    filter(inspection_type == 'complaint') %>%
    group_by(establishment_type, risk_category, year, week, census_block) %>%
    summarise(value=n()) %>%
    mutate(restaurant_inspection_complaints = 'restaurant_inspection_complaints') %>%
    arrange(restaurant_inspection_complaints, establishment_type, risk_category, year, week, census_block, value)

write_csv(data, paste(args[3],".csv", sep = "")

complaints <- read_csv("./new complaints.csv")
```
