---
title: "Explore Restaurant Inspections Data"
output: html_notebook
---

```{r setup}
library(tidyverse)
library(lubridate)

knitr::opts_knit$set(root.dir = "/Users/kathy/Documents/_projects/dc_doh_hackathon")
```

```{r}

inspection_geocode <- read_csv("data/dc_restaurant_inspections/inspections_geocoded.csv")
inspection_summary <- read_csv("data/dc_restaurant_inspections/potential_inspection_summary_data.csv")
inspection_detail <- read_csv("data/dc_restaurant_inspections/potential_violation_details_data.csv")
```

Let's look at the distribution of days since last inspection to determine typical 
inspeciton frequencies based on risk category.
```{r}

inspection_summary_1 <- inspection_summary %>% 
  arrange(establishment_name, inspection_date) %>% 
  group_by(establishment_name) %>%
  mutate(days_since_last_inspection = as.numeric(inspection_date - lag(inspection_date)))

inspection_summary_1 %>% 
  select(establishment_name, inspection_date, days_since_last_inspection) %>% 
  View()

inspection_summary_1 %>% 
  filter(!is.na(days_since_last_inspection)) %>% 
  ggplot() +
  geom_histogram(aes(days_since_last_inspection)) +
  facet_wrap(~risk_category) +
  xlim(0, 100)
```
Looks like all risk categories peak around 5 days with a steady decrease afterwards.

Maybe it's because we have included follow ups and complaint-based inspections. 
Let's only include routine inspections.
```{r}

inspection_summary_1 %>% 
  ungroup() %>% 
  count(inspection_type) %>% 
  arrange(desc(n))

inspection_summary_1 %>% 
  filter(!is.na(days_since_last_inspection), inspection_type == "Routine") %>% 
  ggplot() +
  geom_histogram(aes(days_since_last_inspection)) +
  facet_wrap(~risk_category) +
  xlim(0, 500)
```

Actually, instead of only plotting routine inspections, we have to re-calculate
days since last inspection to include only routine inspections. 
```{r}
inspection_summary_1 <- inspection_summary %>% 
  filter(inspection_type == "Routine") %>% 
  arrange(establishment_name, inspection_date) %>% 
  group_by(establishment_name) %>%
  mutate(days_since_last_inspection = as.numeric(inspection_date - lag(inspection_date)))

inspection_summary_1 %>% 
  select(establishment_name, inspection_date, days_since_last_inspection) %>% 
  View()

inspection_summary_1 %>% 
  filter(!is.na(days_since_last_inspection)) %>% 
  ggplot() +
  geom_histogram(aes(days_since_last_inspection), binwidth = 30) +
  facet_wrap(~risk_category) +
  xlim(0, 1000)
```
This yields a more clear pattern, although it's still hard to see any distinct cutoffs.

Let's look at where the deciles fall for each risk category.
```{r}
p = seq(0, 1, 0.1)

inspection_summary_1 %>% 
  ungroup() %>% 
  group_by(risk_category) %>% 
  summarise(quantiles = list(sprintf("%1.0f%%", p*100)),
            days = list(quantile(days_since_last_inspection, p, na.rm = TRUE))) %>% 
  unnest() %>% 
  spread(quantiles, days)
```
Ok, it looks like it will be hard to set cutoffs based on, say, the 90th percentile
of days between inspections, because it looks like other than category 1, the rest
of the categories are inspected at about the same frequency. It also looks like there
is a wide range of inspection frequencies within each category.

For now it's use some placeholders...
- Category 1: 900 days
- Category 2-5: 600 days

Next I want to look at the date range of the file.
```{r}
range(inspection_summary_1$inspection_date, na.rm = TRUE)
```

These dates don't make sense. Let's look at the first and last few dates.
```{r}
dates <- inspection_summary_1 %>% 
  count(inspection_date) %>% 
  arrange(inspection_date)

head(dates, 50)
tail(dates, 50)
```
Looks like there are a few dates in 2006/2017, but the inspections really start
in earnest in 2008. Also, the last inspection appears to be on 2017-09-11. So,
let's make our weekly periods start around 2018-01-01 and end around 2017-09-11.



